Nirdizati: A Web-based Tool for Predictive Process Monitoring

### 2017-06-16 BPM17-demo-paper/paper.tex
revise intro

\begin{abstract}
In this paper, we present a prototype of a predictive process monitoring engine for process workers and operational managers.
The developed solution, named \emph{Nirdizati}, is a configurable full-stack web application that supports users in selecting the preferred prediction method from the list of implemented methods and enables the continuous prediction of various performance indicators at runtime.
The results of the predictions, as well as the real-time summary statistics about the process execution, are presented in a dashboard that offers multiple visualization options.
The target audience of this demonstration includes process mining researchers as well as practitioners interested in exploring the potential of process monitoring.
\keywords{Process Mining, Predictive Process Monitoring, Machine Learning}
\end{abstract}

\section{Introduction} \label{sec:intro}

@@

%\vspace{-\baselineskip}
\begin{figure}[t]%[H]
	\centering
	\includegraphics[width=0.7\textwidth]{img/nirdizati-training-architecture}
	\caption{A high-level overview of Nirdizati Training.}
	\label{fig:RNNexample}
\end{figure}
%\vspace{-\baselineskip}

@@

Based on this data flow diagram, we devise the main parts and high-level components of the system (Figure~\ref{fig:arch}):

@@

\begin{figure}
	\centering
	\includegraphics[width=1\textwidth]{img/nirdizati-runtime-architecture}
	\caption{Proposed system design architecture}
	\label{fig:arch}
	%	\vspace{-5\baselineskip}
\end{figure}

@@

\section{Conclusion} \label{sec:conclusion}
The source code has been released as open source software under the Lesser GNU Public License (L-GPL) at \url{http://github.com/nirdizati}. The developed engine has been deployed on the server belonging to the Institute of Computer Science and can be accessed at \url{http://nirdizati.com}.
\bibliographystyle{splncs03}
\bibliography{paper}

>>>>

\begin{abstract}
In this paper, we present Nirdizati, an open-source tool for predictive monitoring of business processes.
The tool can be used to predict the outcome, the next events, or the remaining time of each case of a process.
For example, in an lead-to-order process, Nirdizati can predict which customer leads will convert to purchase orders and when.
In a claims handling process, Nirdizati can predict if a claim decision will be made on time or late.
Based on these predictions, process workers and operational managers can act proactively to resolve or mitigate potential process performance violations.
The target audience of this demonstration includes process mining researchers as well as practitioners interested in exploring the potential of process monitoring.
\keywords{Process Mining, Predictive Process Monitoring, Machine Learning}
\end{abstract}

\section{Introduction} \label{sec:intro}
Nirdizati consists of two components: Nirdizati Training and Nirdizati Runtime (Figure~\ref{fig:nirdizati-overall}). Nirdizati Training takes as input a business process event log and produces a prediction model. This model can then be deployed in Nirdizati Runtime. Once a model is deployed, Nirdizati Runtime listens to a stream of events related to a business process, and produces a stream of predictions. These predictions are then visualized in a continuously updated Web dashboard.

%\vspace{-\baselineskip}
\begin{figure}[t]%[H]
	\centering
	\includegraphics[width=0.7\textwidth]{img/nirdizati-overall}
	\caption{A high-level overview of Nirdizati.}
	\label{fig:nirdizati-overall}
\end{figure}
%\vspace{-\baselineskip}

@@

%\vspace{-\baselineskip}
\begin{figure}[t]%[H]
	\centering
	\includegraphics[width=0.7\textwidth]{img/nirdizati-training}
	\caption{A high-level overview of Nirdizati Training.}
	\label{fig:nirdizati-training}
\end{figure}
%\vspace{-\baselineskip}

@@

Based on this data flow diagram, we devise the main parts and high-level components of the system (Figure~\ref{fig:nirdizati-runtime}):

@@

\begin{figure}
	\centering
	\includegraphics[width=1\textwidth]{img/nirdizati-runtime}
	\caption{Proposed system design architecture}
	\label{fig:nirdizati-runtime}
	%	\vspace{-5\baselineskip}
\end{figure}

@@

\section{Conclusion} \label{sec:conclusion}
The developed solution, named \emph{Nirdizati}, is a configurable full-stack web application that supports users in selecting the preferred prediction method from the list of implemented methods and enables the continuous prediction of various performance indicators at runtime.
The results of the predictions, as well as the real-time summary statistics about the process execution, are presented in a dashboard that offers multiple visualization options.

The source code has been released as open source software under the Lesser GNU Public License (L-GPL) at \url{http://github.com/nirdizati}. The developed engine has been deployed on the server belonging to the Institute of Computer Science and can be accessed at \url{http://nirdizati.com}.
\bibliographystyle{splncs03}
\bibliography{paper}
